### 2015-07-14 text/ms.Rmd
Rework paper after co-author comments

@@

\noindent
Sean C. Anderson^1\*^, 
Andrew B. Cooper^1^,
Olaf P. Jensen^4^, 
C\'{o}il\'{i}n Minto^6^, 
James T. Thorson^11^,
Jessica C. Walsh^1^,
Jamie Afflerbach^2^, 
Mark Dickey-Collas^3^, 
Kristin M. Kleisner^5^, 
Catherine Longo^2^, 
Giacomo Chato Osio^7^, 
Dan Ovando^8^, 
Andrew A. Rosenberg^9^, 
Elizabeth R. Selig^10^

@@

\noindent
^3^International Council for the Exploration of the Sea

@@

@@

<!--up to 350 words-->

Ecological resource managers are often faced with reconciling multiple potentially
conflicting estimates of population status and trajectory. One solution is to
average these predictions in an ensemble, but this approach ignores covariance
between models and may not optimally reduce bias and improve accuracy.
Superensemble models, commonly used for climate and weather
forecasting, may provide a superior solution. Superensembles use the predictions
from multiple models as covariates in a new statistical model. Here we evaluate
the potential for ensemble and superensemble models ('ensemble methods') to improve estimates of fish population
status and trajectory. We fit four data-limited models of population and exploitation
dynamics to marine fish stocks and combine their estimates of the mean and
slope of biomass at maximum sustainable yield ($B/B_\mathrm{MSY}$) with an
ensemble average and three superensembles: a linear model, a random forest, and
a boosted regression tree. 
We selected data-limited models for their applicability across the majority of fish stocks world wide.
We build our models on a simulated dataset of 5760
stocks and tested them with cross-validation and a global database of 
`r ram_stocks_n` stock assessments that have also been assessed with more data-intensive stock assessment models.
We find that ensemble methods substantially improve estimates of population status and trajectory.
Machine-learning superensembles performed the best for population status: accuracy improved
`r mean_sim$mach_vs_ind_mare_fold`%, correlation between predicted and true
status improved from 
`r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and bias (median
proportional error) declined from 
`r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. 
We found similar improvements when predicting the trajectory of status. When the
simulation-trained superensembles were applied to catch data for global fish stocks, the best
superensembles improved all dimensions of performance over the next-best
individual model. Ensemble methods have the potential to
improve estimates of population status and trajectory across many taxa beyond
fish. However, they must be carefully tested, formed from a diverse set of
accurate models, and built on a dataset sufficiently representative of the
populations to which they are applied.

\bigskip
<!-- up to 12 keywords -->
\noindent 
Keywords: data-limited fisheries, ensemble methods, multi-model averaging, population dynamics, sustainable resource management

@@

Population status and trajectory are two of the most fundamental values to quantify in ecological resource management [e.g. @mace2008; @iucn2015]. These properties are key to everything from global assessments of extinction risk [e.g. @stuart2004; @schipper2008] to assessing hunting and fishing exploitation levels [e.g. @worm2009; @juan-jorda2011]. However, ecological resource managers are often faced with reconciling multiple uncertain and potentially conflicting estimates of status and trajectory [e.g. @brodziak2010; @branch2011]. Some models may suggest a population is at risk and declining in abundance while others may suggest it is not at risk and stable.

One solution is to take the average or weighted average of an ensemble of model predictions. Such ensembles are typically more accurate and less biased than individual model estimates and can integrate uncertainty in model structure, initial conditions, and parameter estimation [@dietterich2000; @araujo2007]. This approach forms the basis of many machine learning methods [e.g. @dietterich2000], has helped reconcile climate forecasts from dozens of models [e.g. @murphy2004; @tebaldi2007; @ipcc2013], and even improved early warning signs of malaria outbreaks [@thomson2006]. In ecology, ensemble methods are frequently used to improve species distribution modelling [e.g. @araujo2007; @breiner2015] and indeed have been used to combine estimates of population status and trajectory [e.g. @brodziak2010] COSEWIC-IUCN REFS.

<!--
Biological ensemble modeling to evaluate potential futures of living marine resources
Anna Gårdmark1,8, Martin Lindegren2, Stefan Neuenfeldt2, Thorsten Blenckner3, Outi Heikinheimo4, Bärbel Müller-Karulis3,5, Susa Niiranen3, Maciej T. Tomczak3, Eero Aro4, Anders Wikström6, and Christian Möllmann7
Read More: http://www.esajournals.org/doi/abs/10.1890/12-0267.1
-->

Whereas averages or weighted averages may improve predictions over any single model, they may not optimally leverage available data. The truth does not necessarily lie in the middle of multiple model predictions, some models may perform better than others in certain conditions, and the covariance between models may contain information that can improve predictive accuracy. We can exploit these characteristics by using the predictions from a group of models as inputs into a separate statistical model. This technique, sometimes called 'superensemble' modelling [@krishnamurti1999], is common in climate and weather forecasting [e.g. @yun2005; @mote2015]. The superensemble is fit to some training dataset where outcomes are well known and used to predict on a dataset of interest. For example, @krishnamurti1999 combined predictions of wind and precipitation in Asian monsoons via a superensemble regression fit to observed data. Their superensemble was considerably more accurate than any individual prediction or weighted average of predictions.

<!-- Ensemble methods, which combine the output from multiple models as
predictors in a new 'ensemble' model, are one possible solution to this
problem. A simple ensemble model might take the average of multiple model
predictions, perhaps weighted by some goodness of fit. A complex ensemble model
might also take into account non-linear interactions between model predictions
and additional covariates. Ensemble models are popular in other fields
including public health [@thomson2006], agriculture [@cantelaube2005], climate
science [@murphy2004; @tebaldi2007; @pierce2009], and machine learning
[@dietterich2000].-->

In fisheries science, the gold standard for determining status and trajectory
of exploited fish populations are stock assessments that
incorporate all available data (e.g. catches, size and age distributions,
surveys, and tagging information) to quantify values such as 
the biomass that can produce maximum sustainable yield ($B/B_\mathrm{MSY}$).
However, these kinds of data are not available for the majority of fish
populations
[@fao2014]. Therefore, a number of models have been proposed to assess
$B/B_\mathrm{MSY}$ based on the limited data available for the majority of
fish stocks: catches and a basic understanding of population productivity [e.g.
@vasconcellos2005; @martell2013]. Recently, @rosenberg2014 investigated the
performance of four data-limited models through a large-scale simulation
experiment. The four models frequently disagreed about population status and
any one model had relatively poor predictive ability on average (e.g. Fig.
\ref{motivate}).

@@

We first developed and tested ensemble methods with a fully factorial simulated
dataset [@rosenberg2014] with precisely known status. These published simulations included three life
histories: small pelagic, demersal, and large pelagic; three levels of how
depleted biomass was at the start of the dataset compared to carrying capacity:
100%, 70%, and 40% of carrying capacity; and four exploitation dynamics: a
constant exploitation rate, an exploitation rate coupled with biomass to mimic
an open-access single-species fishery, a scenario where exploitation rate
increases to a fixed level, and a 'roller-coaster' scenario where the
exploitation rate increases and then decreases cyclically. Process noise was
introduced to the models through two levels of multiplicative recruitment
variability: $N(0, 0.2)$ and $N(0, 0.6)$, and was either
uncorrelated or had a first-order autoregressive correlation of $0.6$. The
simulation included a scenario without observation error and with
multiplicative observation error around catch at $N(0, 0.2)$.

@@

  <!--TODO: build in fig:didactic -->

@@

Superensemble models allow us to incorporate additional covariates 
and potentially leverage interactions between these covariates and individual
model predictions. Additional covariates could be, for example, life-history
characteristics, information on exploitation patterns, or statistical
properties of the data. For simplicity, and to allow us to apply models
developed with the simulated dataset to the real-world dataset, we added only one
set of additional covariates: spectral properties of the catch time series.
Spectral analysis decomposes a time series into the frequency domain and
provides a means of describing the statistical properties of the catch series
that is independent of time series length and absolute magnitude of catch. We fit
spectral models to the scaled catch time series (catch divided by maximum
catch) with the `spec.ar` function in \textsf{R} and recorded representative
short- and long-term spectral densities at frequencies of 0.20 and 0.05, which
correspond to 5- and 20-year cycles.

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations [e.g. @walther2005]. Here,
we measure proportional error, defined as
$(\hat{b} - b)/b$, where $\hat{b}$ and $b$ represent estimated and 'true'
(or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional
error to measure bias, median absolute proportional error to measure accuracy,
and Spearman's rank-order correlation to measure the ability to correctly rank
populations. Code to reproduce our analysis is available at
<https://github.com/datalimited/ensembles>.

@@

Ensemble methods, and in particular the machine learning superensemble models (random
forest and GBM), generally improved estimates of status and trajectory over any individual model (Fig.
\ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the
individual models, machine learning superensembles improved accuracy (median
absolute proportional error) by 
`r mean_sim$mach_vs_ind_mare_fold`%, 
increased rank-order correlation from `r mean_sim$ind_corr_range` 
to `r mean_sim$mach_corr_range`, 
and reduced bias (median proportional error) from 
`r mean_sim$ind_mre_range` to 
`r mean_sim$mach_mre_range` (Fig. \ref{performance}a). 
These superensembles also had better ability to distinguish if
simulated stocks were above or below $B/B_\mathrm{MSY} = 1$ (Fig.
\ref{roc-sim}). Results were similar when predicting trajectory: compared to
individual models, machine learning superensembles improved accuracy by 
`r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from 
`r slope_sim$ind_corr_range` to 
`r slope_sim$mach_corr_range`, and reduced bias
from `r slope_sim$ind_mre_range` 
to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The
ensemble models that simply took a mean of the individual models ranked
slightly behind the best individual model for estimating fish stock status (CMSY; Fig.
\ref{performance}a) and had slightly lower correlation but higher accuracy than
the best individual model at predicting the trends of status (SSCOM; Fig.
\ref{performance-sim-slope}).

@@

Ensemble methods provide a useful approach to situations where conservation and
ecological resource management decisions must be made on the basis of multiple,
potentially contrasting estimates of status---a situation common to many
ecological settings beyond fisheries. Compared to individual models of fish
population status, ensemble methods were consistently the best or among the best
across three performance dimensions (accuracy, bias, and rank-order
performance), two response variables (status and trajectory), two datasets
(simulated and global fisheries), and multiple ensemble methods (from a
simple average to machine learning superensembles). Our results suggest choosing an
superensemble model that allows for non-parametric relationships, such as machine
learning methods. These methods provide added insight into individual model
behaviour and generally performed the best, however even a simple average of
predictions across multiple models may be a robust solution compared to picking
any one model.

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, or make errors in
uncorrelated ways [@ali1996; @dietterich2000; @tebaldi2007]. Such
individual models would be expected to perform well in different conditions and
an ensemble model can exploit the best predictive performance of each. Second,
ensemble models will be most effective when they are not overfit to the
training dataset. Cross-validation testing [@caruana2004; @hastie2009] and
methods that are robust to over-fitting such as random forests [@breiman2001],
may help avoid overfitting ensemble models. We note that our simplest ensemble
model, an average of individual model predictions, performed approximately as
well as complex machine learning models when we applied our ensembles to an
entirely new dataset (Fig. \ref{performance}b) and averages are a common
ensemble approach in climate science [@ipcc2013]. Third, ensemble
models will be most effective when they are trained on data that are
representative of the dataset of interest [@knutti2009; @weigel2010].
Cross-validation within a training dataset will provide an optimistically biased
impression of predictive performance if the training dataset fundamentally
differs from the dataset of interest [@hastie2009].

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criteron (AIC) is a
common analytical approach in ecology [@burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble methods
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890]. A
fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. By focussing on
predictions, ensembles do not suffer from the muddled inference of coefficient
averaging when coefficients covary [@cade2015] and are a more general purpose
tool: they do not require information theoretics, they can combine different
types of models (e.g. parametric and non-parametric models or frequentist and
Bayesian predictions), and they can combine predictions in complex non-linear
ways that may depend on additional covariates.

A strength of superensembles is that they can be tailored to predict specific response
variables. For example, we built separate superensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For example, SSCOM contributed little to the GBM superensemble estimate
of status at higher levels of predicted $B/B_\mathrm{MSY}$, but contributed
strongly to estimates of slope (Fig. \ref{fig:partial-sim-slope}). Formally,
fitting superensemble models to
specific quantities of interest provides an additional calibration step
[@rykiel1996]. Individual models are typically calibrated (i.e. parameters are
estimated) based on a single response variable; however, this model might then
provide a biased or inaccurate estimate of other quantities of interest. For
example, a data-limited fisheries model might calibrate parameters by
maximizing likelihood with respect to observed and predicted catches but those
parameters may then provide a biased or inaccurate estimate of the mean and
slope of $B/B_\mathrm{MSY}$. Ensemble methods provide a final calibration step
to a quantity of interest. This ensemble calibration could further include a
loss function tailored to the goals of the model, say placing greater weight on
accuracy at low status levels than higher values.

*TODO: Coilin: How ensembles can help understand mechanistic underpinnings of individual models*
Beyond predictive performance, superensembles can help understand mechanistic
underpinnings of individual models. 
First, superensembles that allow for nonlinear
relationships can describe at what ranges of a prediction a certain model is
most informative. For example, we can see that SSCOM is most effective at
distinguishing low values of $B/B_\mathrm{MSY}$ (Fig. S4).
Second, the interaction between superensemble predictors can highlight
under what conditions certain models perform best. 
For instance, SAY SOMETHING ABOUT FIG S5 or FIG S6.
*discover surprises: counterintuitive relationships and interactions*
*can dig into surprising conditions and learn about why certain models fail; potentially learn how to improve models*
*can learn under what conditions certain models perform well*

Combining predictions from multiple models via superensemble methods is also
broadly useful in other subfields of ecology and fisheries science. Predictions
about extinction risk are widely used at the national (e.g. the US Endangered
Species Act and the Canadian Species at Risk Act) and international [e.g. the
IUCN Red List, @iucn2015] levels. These risk assessments generally involve
fitting regression models to outcomes for individual species along with
predictors of species risk [e.g. @anderson2011a; @pinsky2011], or
population dynamics models to data for individual species [e.g. @dfo2010].
Both types of models are prone to error caused by model-misspecification and
therefore results are sensitive to decisions about model structure
[@brooks2015]. Although there are options to account for potential
model-misspecification in determination of species risk (e.g., coefficient
averaging, [@burnham2002], generalized modeling [@yeakel2011], or
semi-parametric methods, [@thorson2014]), ensemble methods are a relatively
simple way to combine predictions in a transparent manner. Beyond estimates of
status and trajectory, ensemble methods could be used to increase the robustness
of spatial predictions when designing networks of protected areas
[@rassweiler2014], or to forecast potential spatial shifts in species
distribution given climate impacts [@harsch2014].

<!--
* Other possible topics:
    * how much better are the ensembles really? translate the results into
      some concrete examples in an absolute not relative sense
    * other types of ensembles: assigning weights, incorporating uncertainty
      around estimates, GAMs, ...
    * when wouldn't you want to use ensembles? perhaps if models represent 
      dichotomous assumptions where either one or the other is right and imply
      different management actions? ...
    * your ideas here...

>>>>

<!--notes:
http://onlinelibrary.wiley.com/journal/10.1111/(ISSN)1523-1739/homepage/ForAuthors.html

con bio: American spelling

Contributed Papers: 6000 words

Submit your cover page as a separate document. It should not be part of the
manuscript itself. The cover page must include the title of the paper; a running
head (short title of 40 or fewer characters); a list of 5-8 keywords; word count
(all text from the first word of the Abstract through the last word of the
Literature Cited but not including table or figure legends or the body of
tables); authors' complete mailing addresses (including postal code) at the time
the work was conducted and present addresses if different; name and complete
address (including email) of the person to whom correspondence should be sent;
and text of your acknowledgments section.

Contributed Papers, Research Notes, and Conservation Practice and Policy papers
should contain the following sections in the following order: Abstract,
Introduction, Methods, Results, Discussion, Supporting Information paragraph (if
there are online appendices), Literature Cited, tables, figure legends, and
figures. Do not combine sections (e.g., Results and Discussion). The
Acknowledgments section will be added to the body of the paper after the
manuscript has been accepted. Do not number section headings or subheadings. Do
not include a Conclusion section (conclusions are part of the Discussion).

You may have color figures in the online version and gray-scale figures in
print. However, reference to color cannot be made in the figure legend or in the
text, and elements in the gray-scale version must be distinguishable. Supply
separate files for color and gray-scale figures.

-->

@@

\noindent
Sean C. Anderson^1\*^, 
Andrew B. Cooper^1^,
Olaf P. Jensen^4^, 
C\'{o}il\'{i}n Minto^6^, 
James T. Thorson^11^,
Jessica C. Walsh^1^,
Jamie Afflerbach^2^, 
Mark Dickey-Collas^3,12^, 
Kristin M. Kleisner^5^, 
Catherine Longo^2^, 
Giacomo Chato Osio^7^, 
Dan Ovando^8^, 
Andrew A. Rosenberg^9^, 
Elizabeth R. Selig^10^

@@

\noindent
^3^International Council for the Exploration of the Sea, 
H.C. Andersens Boulevard 44-46, DK 1553, Copenhagen, Denmark

\noindent
^4^Institute of Marine & Coastal Sciences, Rutgers University, 
71 Dudley Road, New Brunswick, NJ, 08901-8525, USA

@@

\noindent
^12^DTU Aqua National Institute of Aquatic Resources, Technical University of Denmark (DTU), Jægersborg Alle 1, 2920 Charlottenlund, Denmark

@@

<!--up to 300 words-->

Ecological resource managers are often faced with reconciling multiple
potentially conflicting estimates of population status and trajectory. One
solution is to average these predictions in an ensemble, but this approach
ignores covariance between models and may not optimally reduce bias and improve
accuracy. Superensemble models, commonly used for climate and weather
forecasting, may provide a superior solution. Superensembles use the predictions
from multiple models as covariates in a new statistical model. Here we evaluate
the potential for ensemble and superensemble models ('ensemble methods') to
improve estimates of fish population status and trajectory. We fit four
data-limited models of population and exploitation dynamics to marine fish
stocks and combine their estimates of the mean and slope of biomass at maximum
sustainable yield ($B/B_\mathrm{MSY}$) with an ensemble average and three
superensembles: a linear model, a random forest, and a boosted regression tree. 
We selected data-limited models for their applicability across the majority of
fish stocks world wide. We build our models on a simulated dataset of 5760
stocks and tested them with cross-validation and a global database of 
`r ram_stocks_n` stock assessments that have also been assessed with more
data-intensive stock assessment models. We find that ensemble methods
substantially improve estimates of population status and trajectory.
Machine-learning superensembles performed the best for population status:
accuracy improved
`r mean_sim$mach_vs_ind_mare_fold`%, rank-order correlation between predicted
and true status improved from 
`r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and bias (median
proportional error) declined from 
`r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. 
We found similar improvements when predicting the trajectory of status and when
applying the simulation-trained superensembles to catch data for global fish
stocks. Ensemble methods have the potential to improve estimates of population
status and trajectory across many taxa beyond fish. However, they must be
carefully tested, formed from a diverse set of accurate models, and built on a
dataset sufficiently representative of the populations to which they are
applied.

\bigskip
\noindent 
Keywords: data-limited fisheries, ensemble methods, multi-model averaging, population dynamics, sustainable resource management
<!--Include on the cover page five to eight words or phrases that will be useful for indexing and literature searches. Do not use words in the title as keywords, and avoid general terms such as conservation.-->

@@

Population status and trajectory are two of the most fundamental values to
quantify in conservation biology [e.g. @mace2008; @iucn2015]. These properties
are key to everything from global assessments of extinction risk [e.g.
@stuart2004; @schipper2008] to assessing the sustainability of hunting and
fishing exploitation levels [e.g. @worm2009; @juan-jorda2011]. However,
conservation and ecological resource managers are often faced with reconciling
multiple uncertain and potentially conflicting estimates of status and
trajectory [e.g. @brodziak2010; @branch2011]. Some models may suggest a
population is at risk and declining in abundance while others may suggest it is
not at risk and stable.

One solution is to take the average or weighted average of an ensemble of model
predictions. Such ensembles are typically more accurate and less biased than
individual model estimates and can integrate uncertainty in model structure,
initial conditions, and parameter estimation [@dietterich2000; @araujo2007].
This approach forms the basis of many machine learning methods [e.g.
@dietterich2000], has helped reconcile climate forecasts from dozens of models
[e.g. @murphy2004; @tebaldi2007; @ipcc2013], and even improved early warning
signs of malaria outbreaks [@thomson2006]. In ecology, ensemble methods are
frequently used to improve species distribution modelling [e.g. @araujo2007;
@breiner2015] and indeed have been used to combine estimates of population
status and trajectory [e.g. @brodziak2010].

Whereas averages or weighted averages may improve predictions over any single
model, they may not optimally leverage available data. The truth does not
necessarily lie in the middle of multiple model predictions, some models may
perform better than others in certain conditions, and the covariance between
models may contain information that can improve predictive accuracy. We can
exploit these characteristics by using the predictions from a group of models as
inputs into a separate statistical model. This technique, sometimes called
superensemble modelling [@krishnamurti1999], is common in climate and weather
forecasting [e.g. @yun2005; @mote2015]. The superensemble is fit to some
training dataset where outcomes are well known and used to predict on a dataset
of interest. For example, @krishnamurti1999 combined predictions of wind and
precipitation in Asian monsoons via a superensemble regression fit to observed
data. Their superensemble was considerably more accurate than any individual
prediction or weighted average of predictions.

In fisheries science, the commonly used operational model for determining status
and trajectory of exploited fish populations are stock assessments that
incorporate all appropriate data (e.g. catches, size and age distributions,
surveys, and tagging information) to quantify values such as the biomass that
can produce maximum sustainable yield ($B/B_\mathrm{MSY}$). However, a broad
range of data are not available for the majority of fish populations [@fao2014].
Therefore, a number of models have been proposed to assess $B/B_\mathrm{MSY}$
based on the limited data available for the majority of fish stocks: catches and
a basic understanding of population productivity [e.g. @vasconcellos2005;
@martell2013]. Recently, @rosenberg2014 investigated the performance of four
data-limited models through a large-scale simulation experiment. The four models
frequently disagreed about population status and any one model had relatively
poor predictive ability on average (e.g. Fig. \ref{motivate}).

@@

We first developed and tested ensemble methods with a fully factorial simulated
dataset [@rosenberg2014] with precisely known status. These published
simulations included three fish life histories: small pelagic, demersal, and large
pelagic; three levels of how depleted biomass was at the start of the dataset
compared to carrying capacity: 100%, 70%, and 40% of carrying capacity; and four
harvest dynamics: a constant harvest rate, a harvest rate
coupled with biomass to mimic an open-access single-species fishery, a scenario
where harvest rate increases continuously, and a 'roller-coaster'
scenario where the harvest rate increases and then decreases.
Process noise was introduced to the models through two levels of multiplicative
recruitment variability: $N(0, 0.2)$ and $N(0, 0.6)$, and was either
uncorrelated or had a first-order autoregressive correlation of $0.6$. The
simulation included a scenario without observation error and with multiplicative
observation error around catch at $N(0, 0.2)$.

@@

@@

<!--TODO Kristin and Mark: It might be a good idea to add a figure that
illustrates the spectrum of ensemble/superensembles that are applied here and
what is included (e.g., non-linear relationships, etc.). This will help the
reader understand the progression in complexity of the ensemble approaches I
think.-->
Superensemble models allow us to incorporate additional covariates 
and potentially leverage interactions between these covariates and individual
model predictions. Additional covariates could be, for example, life-history
characteristics, information on exploitation patterns, or statistical
properties of the data. For simplicity, and to allow us to apply models
developed with the simulated dataset to the real-world dataset, we added only one
set of additional covariates: spectral properties of the catch time series.
Spectral analysis decomposes a time series into the frequency domain and
provides a means of describing the statistical properties of the catch series
that is independent of time series length and absolute magnitude of catch. We fit
spectral models to the scaled catch time series (catch divided by maximum
catch) with the `spec.ar` function in \textsf{R} and recorded representative
short- and long-term spectral densities at frequencies of 0.20 and 0.05, which
correspond to 5- and 20-year cycles.

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations [e.g. @walther2005]. Here,
we measure proportional error, defined as
$(\hat{b} - b)/b$, where $\hat{b}$ and $b$ represent estimated and 'true'
(or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional
error to measure bias, median absolute proportional error to measure accuracy,
and Spearman's rank-order correlation between predicted and 'true' values to
measure the ability to correctly rank populations. Code to reproduce our
analysis is available at
<https://github.com/datalimited/ensembles>.

@@

Ensemble methods, and in particular the machine learning superensemble models (random
forest and GBM), generally improved estimates of status and trajectory over any individual model (Fig.
\ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the
individual models, machine learning superensembles improved accuracy (median
absolute proportional error) by 
<!--TODO: check these percentage values- right?-->
`r mean_sim$mach_vs_ind_mare_fold`%, 
increased rank-order correlation from `r mean_sim$ind_corr_range` 
to `r mean_sim$mach_corr_range`, 
and reduced bias (median proportional error) from 
`r mean_sim$ind_mre_range` to 
`r mean_sim$mach_mre_range` (Fig. \ref{performance}a). 
These superensembles also had better ability to distinguish if
simulated stocks were above or below $B/B_\mathrm{MSY} = 1$ (Fig.
\ref{roc-sim}). Results were similar when predicting trajectory: compared to
individual models, machine learning superensembles improved accuracy by 
`r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from 
`r slope_sim$ind_corr_range` to 
`r slope_sim$mach_corr_range`, and reduced bias
from `r slope_sim$ind_mre_range` 
to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The
ensemble models that simply took a mean of the individual models ranked
slightly behind the best individual model for estimating fish stock status (CMSY; Fig.
\ref{performance}a) and had slightly lower correlation but higher accuracy than
the best individual model at predicting the trends of status (SSCOM; Fig.
\ref{performance-sim-slope}).

@@

Ensemble methods provide a useful approach to situations where conservation and
ecological resource management decisions must be made on the basis of multiple,
potentially contrasting estimates of status---a situation common to many
ecological settings beyond fisheries. Compared to individual models of fish
population status, ensemble methods were consistently the best or among the best
across three performance dimensions (accuracy, bias, and rank-order
correlation), two response variables (status and trajectory), two datasets
(simulated and global fisheries), and multiple ensemble methods (from a
simple average to machine learning superensembles). Our results suggest choosing an
superensemble model that allows for non-parametric relationships, such as machine
learning methods. These methods provide added insight into individual model
behaviour and generally performed the best; however, even a simple average of
predictions across multiple models may provide a more useful measure of the
desired parameter than a single model in many cases.

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, or make errors in
uncorrelated ways [@ali1996; @dietterich2000; @tebaldi2007]. Such individual
models would be expected to perform well in different conditions and an ensemble
model can exploit the best predictive performance of each. Second, ensemble
models will be most effective when they are not overfit to the training dataset.
Cross-validation testing [@caruana2004; @hastie2009] and methods that are robust
to over-fitting such as random forests [@breiman2001], may help avoid
overfitting ensemble models. We note that our simplest ensemble model, an
average of individual model predictions, performed approximately as well as
complex machine learning models when we trained our superensembles on the
simulation dataset and tested them on a separate 'real' dataset (i.e. the RAM
Legacy Stock Assessment database, Fig. \ref{performance}b). Third, ensemble
models will be most effective when they are trained on data that are
representative of the dataset of interest [@knutti2009; @weigel2010].
Cross-validation within a training dataset will provide an optimistically biased
impression of predictive performance if the training dataset fundamentally
differs from the dataset of interest [@hastie2009].

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criterion (AIC) is a
common analytical approach in ecology [@burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble methods
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890]. A
fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. While the
outcome will be the same in some cases, ensembles provide a more general
purpose tool: they do not require information theoretics and they can combine
different types of models (e.g. parametric and non-parametric models or
frequentist and Bayesian predictions). Furthermore, superensembles extend these
benefits by allowing model predictions be combined in via non-linear functions
that are tuned to known data.

A strength of superensembles is that they can be tailored to predict specific
response variables. For example, we built separate superensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For instance, SSCOM contributed little to the GBM superensemble
estimate of status at higher levels of predicted $B/B_\mathrm{MSY}$, but
contributed strongly to estimates of trajectory (Fig. \ref{partial-sim-slope}).
Formally, fitting superensemble models to specific quantities of interest
provides an additional calibration step [@rykiel1996]. Individual models are
typically calibrated (i.e. parameters are estimated) based on a single response
variable; however, this model might then provide a biased or inaccurate estimate
of other quantities of interest. Ensemble methods provide a final calibration
step to a quantity of interest. This ensemble calibration could further include
a loss function tailored to the goals of the model, say placing greater weight
on accuracy at low status levels than higher values. Conversely, because
superensembles are tailored to a specific response and loss function,
superensembles force a modeller to choose an operational purpose for their model
up front [*sensu* @dickey-collas2014].

As @box1987 noted, all models are wrong, but they may still be useful. The
ensemble methods we investigated attempt to piece together the useful parts of
candidate models to build a model with improved performance. Instead of viewing
the superensemble as a black box, we think considerable mechanistic
understanding can be gained by studying the structure of the superensemble. For
example, when SSCOM estimates very low status this is likely the case,
conversely when COMSIR estimates low status, the truth is likely that the status
is high (Fig. \ref{partial-sim}). These models have two main differences: (1)
the form of effort dynamics and (2) the allowance for both measurement and
process error in SSCOM, whereas the implemented COMSIR admits measurement error
only. Were the methods to differ only in effort dynamics, the results point
towards a more suitable representation of effort dynamics at low biomasses in
SSCOM. We think that such investigation of the parameters of a superensemble may
lead to improvement in the mechanisms imparted to the individual models.

Combining predictions from multiple models via superensemble methods is also
broadly useful in other subfields of ecology and fisheries science. Predictions
about extinction risk are widely used at the national (e.g. the US Endangered
Species Act and the Canadian Species at Risk Act) and international [e.g. the
IUCN Red List, @iucn2015] levels. These risk assessments generally involve
fitting regression models to outcomes for individual species along with
predictors of species risk [e.g. @anderson2011a; @pinsky2011], or population
dynamics models to data for individual species [e.g. @dfo2010]. Both types of
models are prone to error caused by model-misspecification and therefore results
are sensitive to decisions about model structure [@brooks2015]. Although there
are options to account for potential model-misspecification in determination of
species risk [e.g. coefficient averaging, @burnham2002; generalized modeling,
@yeakel2011; or semi-parametric methods, @thorson2014], ensemble methods are
a relatively simple way to combine predictions in a transparent manner. Beyond
estimates of status and trajectory, ensemble methods could be used to increase
the robustness of spatial predictions when designing networks of protected areas
[@rassweiler2014], or to forecast potential spatial shifts in species
distribution given climate impacts [@harsch2014].

<!--

and different models may result in different scalings of population status
[Deroba JJ, Butterworth DS, Methot RD Jr., De Oliveira JAA, Fernandez C, Nielsen
A, Cadrin SX, Dickey-Collas M, Legault CM, Ianelli J, et al. 2015. Simulation
testing the robustness of stock assessment models to error: some results from
the ICES Strategic Initiative on Stock Assessment Methods. ICES Journal of
Marine Science 72: 19–30 doi:10.1093/icesjms/fst237]
CM: It would be good to keep this in mind from a management perspective as
depending on the assumptions in the assessment, biomass could be high and
fishing mortality low to predict the same catches as biomass low and fishing
mortality high. Combining for a single scaled variable B/Bmsy removes some of
the scaling but when there is a strong covariation in B and F this would need to
be (and likely can be) accounted for in a bivariate ensemble. Not our focus here
but could enter the Discussion.

Biological ensemble modeling to evaluate potential futures of living marine
resources
Anna Gårdmark1,8, Martin Lindegren2, Stefan Neuenfeldt2, Thorsten Blenckner3,
Outi Heikinheimo4, Bärbel Müller-Karulis3,5, Susa Niiranen3, Maciej T. Tomczak3,
Eero Aro4, Anders Wikström6, and Christian Möllmann7
Read More: http://www.esajournals.org/doi/abs/10.1890/12-0267.1

* Other possible topics:
    * how much better are the ensembles really? translate the results into
      some concrete examples in an absolute not relative sense
    * other types of ensembles: assigning weights, incorporating uncertainty
      around estimates, GAMs, ...
    * when wouldn't you want to use ensembles? perhaps if models represent 
      dichotomous assumptions where either one or the other is right and imply
      different management actions? ...
    * your ideas here...
